<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-02-23 cook_sot_march.Rmd
checking plot_conctime
skeleton of poster

```{r, load_data}

@@

```{r, out.width="60%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
knitr::include_graphics("poster/tk_curve.png")
```

@@

## **1c) In-House Curation Workflow**
1) Identify publications with CvT data using PubMed queries

2) Manually extract CvT data using [WebPlotDigitizer](https://automeris.io/WebPlotDigitizer/)

3) Curate CvT data and metadata using EPA's *.xlsx* template

4) Screen template using *CvTdbQA*, an R Shiny application that checks template for format and reconstructs plots based on reported CvT data

5) Manually check template for format and data correctness

6) Normalize metadata units using an R script workflow, while also retaining original values

7) Push template to CvTdb

@@

```{r, make_cvt_variability_histogram}

@@

## **3a What is *invivoPKfit*?**

@@

```{r, out.width="30%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
knitr::include_graphics("poster/pk_workflow.png")
```

## **3b TK Model Descriptions**
|    **<span style="text-decoration:underline">1-Compartment Model</span>**

```{r, fig.cap = "1-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center",  out.width = "60%"}
knitr::include_graphics("poster/1_comp.png")
```

@@

```{r, fig.cap = "2-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center", out.width = "60%"}
knitr::include_graphics("poster/2_comp.png")
```

@@

## **3c Statistical Model Description**

@@

```{r, warning = FALSE, fig.align = "center", out.width = "60%", fig.cap = "Log-Normal Distribution"}
load(file = "poster/lognormal.Rdata")
p9
```

@@

@@

## **4a Predicted Concentrations**

@@

```{r, make_cp_histogram}

@@

## **4b *invivoPKfit* Performance *versus* Data Variability**

>>>>

```{r, load_data, include=FALSE}

@@

```{r, exp_plot, out.width="65%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
knitr::include_graphics("poster/tk_curve.png")
```

@@

@@

```{r, make_cvt_variability_histogram, out.width = "75%", fig.align = "center", fig.cap = "The CvTdb data was grouped into unique combinations of compound/reference/route/dose/timepoint. Groups without replicate timepoints were removed. If all replicate timepoints corresponded to non-detect concentration values, those data were removed. If some, but not all replicate timepoints corresponded to non-detect concentration values, those values were set to equal 0.45 of the minimum value. Each concentration was normalized by the mean concentration of each group."}

@@

## **3a) What is *invivoPKfit*?**

@@

```{r, workflow, out.width="30%", fig.align="center", fig.cap="Typical plot from which CvT data is extracted. From Sowa and Steibert (1985)."}
knitr::include_graphics("poster/pk_workflow.png")
```

## **3b) TK Model Descriptions**
|    **<span style="text-decoration:underline">1-Compartment Model</span>**

```{r, 1_comp, fig.cap = "1-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center",  out.width = "75%"}
knitr::include_graphics("poster/1_comp.png")
```

@@

```{r, 2_comp, fig.cap = "2-Compartment Model. Adapted from Wambaugh et al. (2018).", fig.align = "center", out.width = "75%"}
knitr::include_graphics("poster/2_comp.png")
```

@@

## **3c) Statistical Model Description**

@@

```{r, log, warning = FALSE, fig.align = "center", out.width = "60%", fig.cap = "Log-Normal Distribution"}
load(file = "poster/lognormal.Rdata")
p9
```

@@

|    **<span style="text-decoration:underline">Interstudy Variability</span>**

```{r, interstudy, fig.align = "center", out.width = "100%", fig.cap = "Log-Normal Distribution"}
knitr::include_graphics("poster/interstudy.png")
```

@@

## **4a) Predicted Concentrations**

@@

```{r, make_cp_histogram, fig.align = "center", out.width = "75%", fig.cap = "Concentrations were predicted by applying estimated model parameters to the timepoints present in the data. Predicted concentrations were normalized by observed concentrations. This plot does not include 'Joint Analysis' models. The red dashed lines mark the 'factor of two' bounds."}

@@

## **4b) *invivoPKfit* Performance *versus* Data Variability**

### 2022-02-23 figures_01312022.Rmd
skeleton of poster

### 2 compartment
junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_12212021),
                      data.set = as.data.table(raw_2comp_12212021),
                      model = "2compartment")

>>>>

### 2 compartment
junk <- plot_conctime(PK.fit.table = as.data.table(pk_output_2comp_02102022),
                      data.set = as.data.table(raw_2comp_02102022),
                      model = "2compartment")
